Modeling the impacts of park access on health outcomes: a utility-based accessibility approach

### 2020-09-25 manuscript/manuscript.Rmd
Minor edits to manuscript, rebuild

Increased physical activity and decreased obesity rates are critical measures of
improvement in public health. Although many have theorized the link between park
access and public, previous literature has produced mixed
findings, perhaps owing to the wide range of accessibility definitions. 
Using New York City as a case study, we presented a
holistic and flexible measurement for park accessibility that compares the
continuous distance to all parks in the region, weighted against the size of the
park and its other amenities, with weights determinable through revealed
preferences. In terms of physical activity, we found a positive relationship
where the least park-accessible tracts have an expected physical activity
participation rate between `r 6 * .01` and `r 6 * .3` percentage points lower than the most
accessible tracts. We also found a suggestive though not significant relationship
between park accessibility and expected obesity rates *in addition to* the effect
of physical activity participation.

>>>>

Increased physical activity and decreased obesity rates are critical measures of
improvement in public health. Although many have theorized the link between park
access and public health, previous literature has produced mixed
findings, perhaps owing to the wide range of accessibility definitions. 
Using New York City as a case study, we presented a
holistic and flexible measurement for park accessibility that compares the
continuous distance to all parks in the region, weighted against the size of the
park and its other amenities, with weights determinable through revealed
preferences. In terms of physical activity, we found a positive relationship
where the least park-accessible tracts have an expected physical activity
participation rate between `r 6 * .01` and `r 6 * .3` percentage points lower than the most
accessible tracts. We also found a suggestive though not significant relationship
between park accessibility and expected obesity rates *in addition to* the effect
of physical activity participation.

### 2020-09-25 manuscript/manuscript.tex
Update appendix labels and copy complete source tex file
Minor edits to manuscript, rebuild

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Thu Sep 24 13:27:59 2020
 (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\

@@

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park access and public, previous literature has
produced mixed findings, perhaps owing to the wide range of
accessibility definitions. Using New York City as a case study, we
presented a holistic and flexible measurement for park accessibility
that compares the continuous distance to all parks in the region,
weighted against the size of the park and its other amenities, with
weights determinable through revealed preferences. In terms of physical
activity, we found a positive relationship where the least
park-accessible tracts have an expected physical activity participation
rate between 0.06 and 1.8 percentage points lower than the most
accessible tracts. We also found a suggestive though not significant
relationship between park accessibility and expected obesity rates
\emph{in addition to} the effect of physical activity participation.

@@

\hypertarget{appendix}{%
\subsection{Appendix}\label{appendix}}

>>>>

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Thu Sep 24 14:12:00 2020
 (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\

@@

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park access and public health, previous literature has
produced mixed findings, perhaps owing to the wide range of
accessibility definitions. Using New York City as a case study, we
presented a holistic and flexible measurement for park accessibility
that compares the continuous distance to all parks in the region,
weighted against the size of the park and its other amenities, with
weights determinable through revealed preferences. In terms of physical
activity, we found a positive relationship where the least
park-accessible tracts have an expected physical activity participation
rate between 0.06 and 1.8 percentage points lower than the most
accessible tracts. We also found a suggestive though not significant
relationship between park accessibility and expected obesity rates
\emph{in addition to} the effect of physical activity participation.

@@

\hypertarget{appendix}{%
\subsection{Supplementary Material}\label{appendix}}
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}

### 2020-09-25 manuscript/submission/manuscript.tex
Minor edits to manuscript, rebuild

\textcolor{blue}{
The question of how green space in the urban
environment affects the physical, emotional, and mental well-being of
urban residents is not new to the academic literature. Comprehensive
reviews and analysis of this literature up to 2007 can be had from
\citet{tzoulas2007promoting}, and for the subsequent decade from
\citet{kabisch2015human}. In spite of the depth of this research arena
--- or perhaps because of it --- quantitative approaches for assessing
both health outcomes and access to green space vary widely. It is
therefore not surprising that in a meta-analysis of 20 recent peer
reviewed journal articles exploring the relationship between access to
parks and objectively measured physical activity, \citet{Bancroft2015}
found that five studies reported a significant positive association, six
studies produced mixed results, and nine studies found no association at
all.}

\textcolor{blue}{
Loosely defined, the \emph{accessibility} of an arbitrary place
describes the ease with which people can accomplish activities there.
Accessibility is an abstract concept with tempting quantifiability
\citep{Handy1997}, but objective quantification may not be strictly
necessary. For example, \citet{takano2002urban} showed improved survival
rates among senior citizens in Japan who self-reported having access to
qualitatively good walking spaces. Though encouraging, this result could
simply reveal self-selection: Those seniors who felt the walking space
was good were those who chose to enjoy it. Urban planners seeking to
evaluate which residents have good access to quality green space may
desire objective and therefore comparable measures.}

@@

Applications of this isochrone-based framework are easily derived and
relatively common. ParkScore \citep{parkscore2019} is a sophisticated
application of this approach where \(D\) is a carefully calculated
10-minute network-bound walk, paired with a demographic analysis of
areas within and outside of this threshold. \textcolor{blue}{\citet{devries2003natural}
showed the amount of greenspace within a 3-kilometer radius was
positively associated with a suite of self-reported health outcomes.
Similarly, \citet{devries2013streetscape} showed that streetscape
greenery within 500 meters of a residence was associated with perceived
general health. Conversely, \citet{carlson2012interactions} found no
relationship between the health of senior citizens and the number of
parks within 500 meters.}

Another common access measure fits in this category, where
distance-based isochrones are replaced with political, geographical, or
statistical boundaries. \textcolor{blue}{For example, \citet{Mitchell2008} find that inequalities
in health outcomes attributable to income are mitigated in statistical areas
with a greater percentage of green space. \citet{Stark2014} found a significant
relationship in New York City between the percent of a residential ZIP code that
is park space and objectively measured body mass index (BMI).} Political or
regional boundaries are
especially common in comparative macroscopic studies, such as the
positive relationships found by \citet{West2012} between density of park
land in a metropolitan area and self-reported population health
indicators derived from the Behavioral Risk Factor Surveillance System
(BRFSS). On the other hand, \citet{Larson2016} found no relationship
between physical health and park quantity, quality, and accessibility in
44 U.S. cities and self-reported scores on the Gallup-Healthways
Wellbeing Index. It is also possible to attenuate an isochrone with
various factors; for instance, \citet{Dias2019} considered road safety
perception as an extenuating factor in the effective distance to a park.

In spite of the flexibility of adapted isochrone techniques, the
arbitrary definitions necessarily imposed by researchers in its
application can inhibit holistic analysis \citep{Logan2017}. A somewhat
more complete approach is the so-called ``gravity'' accessibility
statistic. In this case the accessibility of point \(i\) is the
denominator of the gravity formulation of a trip distribution model,
\begin{equation}\label{eq:gravity}
A_i = \sum_{j = 1}^J S_j f(d_{ij})
\end{equation} where \(S_j\) is the ``size'' of each park literally
(i.e.~acres) or abstractly (i.e. trip attractions) and \(f(d_{ij})\) is
a monotonically decreasing cost function, usually a negative
exponential. \citet{Dong2006} note that the isochrone framework is a
special case of the gravity model where \(f(d_{ij})\) is a binary
function and \(S_j = 1\). \citet{Giles-Corti2005} compare various
gravity-based accessibility scores with an isochrone specification and
show that the former are more predictive of walking behavior; that is,
the attributes of a park influence walking more than merely the distance
to it. \textcolor{blue}{\citet{hillsdon2006relationship} found no relationship between a
gravity-based accessibility term and self-reported physical activity
among middle-aged individuals in Norwich, England.} \citet{Zhang2011}
developed a population-weighted, gravity-based accessibility to parks
metric with a national scope, though they do not examine its correlation
with health outcomes.

@@

To our knowledge, there has been no previous attempt to examine access
to parks in a metropolitan area using a utility-based definition as the
primary indicator of access. Consequently, there has also been no
previous effort to examine the effect of park access on health outcomes
using this theoretically attractive technique. In this study, we first
develop a utility-based measure of park access in New York City, and
then apply this measure to study the effect of access to public parks on
aggregate health outcomes.

@@

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. The set of amenities we included in the
utility calculation --- and the contribution of each amenity to the
overall utility --- was dictated by the availability of open data on the
park amenities in New York City and our ability to find comparable prior
studies with transferable utility parameters. It is remarkable that our
two utility specifications --- one with size and distance, and one with
size and distance plus amenities --- result in such similar model
estimates. This may indicate that the utility is driven largely by size
and distance, or that the additional park amenities we included in the
utility specification are spatially distributed in a way that correlates
with the health outcomes. Either way, further analysis examining more
amenity variables is warranted. We can envision a study where mobile
device data revealing the home locations of park users would be paired
with more detailed park amenities and use data (e.g.~geolocated Twitter
data \emph{a la} \citet{roberts2017using}) to estimate the utility
contribution of these features. This could in turn provide a more
nuanced understanding of the relationship between park accessibility,
use, and health outcomes.

As a travel impedance measure, we used the Euclidean distance between
each tract's population-weighted centroid and the nearest point on the
edge of a park's border. Euclidean distances have well-rehearsed
limitations regarding their fidelity with the underlying infrastructure
network, etc. Network-based distances can also suffer from challenges
when applied to multimodal problems; these challenges are exacerbated
when the non-highway mode share is high, as is likely when considering
access to parks. We examined replacing the Euclidean distance with a
network-based distance; the choice of distance metric appeared
inconsequential to our larger findings in this case while substantially
increasing the computational load required. Additionally, we could not
verify the accuracy of the underlying network data at the scale of this
analysis. We therefore retain the Euclidean distance for simplicity. A
better metric of travel impedance may be a mode choice model logsum,
which weights all alternative travel alternatives against each other. We
leave this as a recommendation for future research.

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted. We acknowledge that a utility-based framework
for access may be more technically difficult for some practitioners to
independently construct for their analyses than an isochrone or even a
gravity-based measure. That said, it may not be necessary for practicing
planners to construct this measure themselves: web-based tools such as
ParkIndex \citep{Kaczynski2016} and even WalkScore
(\url{https://www.walkscore.com}) abstract complex methodologies into
tools that planners can and do readily apply.

>>>>

The question of how green space in the urban
environment affects the physical, emotional, and mental well-being of
urban residents is not new to the academic literature. Comprehensive
reviews and analysis of this literature up to 2007 can be had from
\citet{tzoulas2007promoting}, and for the subsequent decade from
\citet{kabisch2015human}. In spite of the depth of this research arena
--- or perhaps because of it --- quantitative approaches for assessing
both health outcomes and access to green space vary widely. It is
therefore not surprising that in a meta-analysis of 20 recent peer
reviewed journal articles exploring the relationship between access to
parks and objectively measured physical activity, \citet{Bancroft2015}
found that five studies reported a significant positive association, six
studies produced mixed results, and nine studies found no association at
all.

Loosely defined, the \emph{accessibility} of an arbitrary place
describes the ease with which people can accomplish activities there.
Accessibility is an abstract concept with tempting quantifiability
\citep{Handy1997}, but objective quantification may not be strictly
necessary. For example, \citet{takano2002urban} showed improved survival
rates among senior citizens in Japan who self-reported having access to
qualitatively good walking spaces. Though encouraging, this result could
simply reveal self-selection: Those seniors who felt the walking space
was good were those who chose to enjoy it. Urban planners seeking to
evaluate which residents have good access to quality green space may
desire objective and therefore comparable measures.

@@

Applications of this isochrone-based framework are easily derived and
relatively common. ParkScore \citep{parkscore2019} is a sophisticated
application of this approach where \(D\) is a carefully calculated
10-minute network-bound walk, paired with a demographic analysis of
areas within and outside of this threshold. \citet{devries2003natural}
showed the amount of greenspace within a 3-kilometer radius was
positively associated with a suite of self-reported health outcomes.
Similarly, \citet{devries2013streetscape} showed that streetscape
greenery within 500 meters of a residence was associated with perceived
general health. Conversely, \citet{carlson2012interactions} found no
relationship between the health of senior citizens and the number of
parks within 500 meters.

Another common access measure fits in this category, where
distance-based isochrones are replaced with political, geographical, or
statistical boundaries. For example, \citet{Mitchell2008} find that inequalities
in health outcomes attributable to income are mitigated in statistical areas
with a greater percentage of green space. \citet{Stark2014} found a significant
relationship in New York City between the percent of a residential ZIP code that
is park space and objectively measured body mass index (BMI). Political or
regional boundaries are
especially common in comparative macroscopic studies, such as the
positive relationships found by \citet{West2012} between density of park
land in a metropolitan area and self-reported population health
indicators derived from the Behavioral Risk Factor Surveillance System
(BRFSS). On the other hand, \citet{Larson2016} found no relationship
between physical health and park quantity, quality, and accessibility in
44 U.S. cities and self-reported scores on the Gallup-Healthways
Wellbeing Index. It is also possible to attenuate an isochrone with
various factors; for instance, \citet{Dias2019} considered road safety
perception as an extenuating factor in the effective distance to a park.

In spite of the flexibility of adapted isochrone techniques, the
arbitrary definitions necessarily imposed by researchers in its
application can inhibit holistic analysis \citep{Logan2017}. A somewhat
more complete approach is the so-called ``gravity'' accessibility
statistic. In this case the accessibility of point \(i\) is the
denominator of the gravity formulation of a trip distribution model,
\begin{equation}\label{eq:gravity}
A_i = \sum_{j = 1}^J S_j f(d_{ij})
\end{equation} where \(S_j\) is the ``size'' of each park literally
(i.e.~acres) or abstractly (i.e. trip attractions) and \(f(d_{ij})\) is
a monotonically decreasing cost function, usually a negative
exponential. \citet{Dong2006} note that the isochrone framework is a
special case of the gravity model where \(f(d_{ij})\) is a binary
function and \(S_j = 1\). \citet{Giles-Corti2005} compare various
gravity-based accessibility scores with an isochrone specification and
show that the former are more predictive of walking behavior; that is,
the attributes of a park influence walking more than merely the distance
to it. \citet{hillsdon2006relationship} found no relationship between a
gravity-based accessibility term and self-reported physical activity
among middle-aged individuals in Norwich, England. \citet{Zhang2011}
developed a population-weighted, gravity-based accessibility to parks
metric with a national scope, though they do not examine its correlation
with health outcomes.

@@

\textcolor{blue}{To our knowledge, there has been no previous attempt to examine access
to parks in a metropolitan area using a utility-based definition as the
primary indicator of access. Consequently, there has also been no
previous effort to examine the effect of park access on health outcomes
using this theoretically attractive technique. In this study, we first
develop a utility-based measure of park access in New York City, and
then apply this measure to study the effect of access to public parks on
aggregate health outcomes.}

@@

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. \textcolor{blue}{The set of amenities we included in the
utility calculation --- and the contribution of each amenity to the
overall utility --- was dictated by the availability of open data on the
park amenities in New York City and our ability to find comparable prior
studies with transferable utility parameters. It is remarkable that our
two utility specifications --- one with size and distance, and one with
size and distance plus amenities --- result in such similar model
estimates. This may indicate that the utility is driven largely by size
and distance, or that the additional park amenities we included in the
utility specification are spatially distributed in a way that correlates
with the health outcomes. Either way, further analysis examining more
amenity variables is warranted.} We can envision a study where mobile
device data revealing the home locations of park users would be paired
with more detailed park amenities and use data (e.g.~geolocated Twitter
data \emph{a la} \citet{roberts2017using}) to estimate the utility
contribution of these features. This could in turn provide a more
nuanced understanding of the relationship between park accessibility,
use, and health outcomes.

As a travel impedance measure, we used the Euclidean distance between
each tract's population-weighted centroid and the nearest point on the
edge of a park's border. Euclidean distances have well-rehearsed
limitations regarding their fidelity with the underlying infrastructure
network, etc. Network-based distances can also suffer from challenges
when applied to multimodal problems; these challenges are exacerbated
when the non-highway mode share is high, as is likely when considering
access to parks. \textcolor{blue}{We examined replacing the Euclidean distance with a
network-based distance; the choice of distance metric appeared
inconsequential to our larger findings in this case while substantially
increasing the computational load required. Additionally, we could not
verify the accuracy of the underlying network data at the scale of this
analysis. We therefore retain the Euclidean distance for simplicity.} A
better metric of travel impedance may be a mode choice model logsum,
which weights all alternative travel alternatives against each other. We
leave this as a recommendation for future research.

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted. \textcolor{blue}{We acknowledge that a utility-based framework
for access may be more technically difficult for some practitioners to
independently construct for their analyses than an isochrone or even a
gravity-based measure. That said, it may not be necessary for practicing
planners to construct this measure themselves: web-based tools such as
ParkIndex \citep{Kaczynski2016} and even WalkScore
(\url{https://www.walkscore.com}) abstract complex methodologies into
tools that planners can and do readily apply.}
